Learning by Teaching a Robot:\\The Case of Handwriting

### 2016-01-13 main.tex
Rephrase paragraph on ethics -- Pierre's suggestion

We initially envisioned our system to be run in the back of a classroom with one
child: this would have allowed an individual, face-to-face remediation approach,
not otherwise tractable for a teacher with 20 pupils.  This is however unlikely
to happen soon. In our experience, the teacher keeps such an important role that
the interaction (and the learning!) would hardly occur if the child is left
alone (or even semi-alone). We can therefore reassure teachers: robots are not
going to replace them any time soon, and the initial feedback that we received
during the focus groups shows that, once explained, our approach make sense and
is indeed welcomed by the teachers themselves.

>>>>

We initially envisioned our system to be run in the back of a classroom with one
child: this would have allowed an individual, face-to-face remediation approach,
not otherwise tractable for a teacher with 20 pupils.  This is however unlikely
to happen soon. In our experience, the teacher/facilitator keeps an instrumental
role during the interaction, and the learning would hardly occur if the child is
left alone (or even semi-alone). The initial feedback that we received from the
teachers during the focus groups confirms this perception: once explained, our
approach make sense to them and is indeed welcomed as a relevant pedagogical
innovation.
